\documentclass[sigconf]{acmart}

\begin{document}
\title{Side of The Road}
\subtitle{Project Proposal}

\author{Aaron Le}
\affiliation{%
  \institution{University of California, Santa Cruz}
}
\email{aadle@ucsc.edu}

\author{Aaron Steele}
\affiliation{%
  \institution{University of California, Santa Cruz}
}
\email{atsteele@ucsc.edu}

\author{Alissa Woo}
\affiliation{%
  \institution{University of California, Santa Cruz}
 }
\email{aawoo@ucsc.edu}

\settopmatter{printacmref=false}
\renewcommand\footnotetextcopyrightpermission[1]{} % removes footnote with conference information in first column
\pagestyle{plain} % removes running headers

\begin{abstract}
An application where college students are able to take pictures of items they find on the side of the road and upload said picture. Each picture will have an optional description, a date of when the picture was taken, and the GPS location of where the picture was taken at, to the service. Other users are able to scroll through a list of uploaded pictures and decide if they would want to get the item. If an item has been retrieved, it will be marked as taken. \\
This helps prevent the waste of what could be perfectly reusable items and easily connects college students who want to get rid of old items to other users who might find use of these items. Users will be able to filter based on distance from their current location, or view thumbnails on a map.
\end{abstract}

\maketitle

\section{Background}
It is common to find unwanted items placed on the side of the road and even more so in college towns. Students are often too lazy to sell their items or believe their items have little to no value and leave furniture on the side of the road that could be used for new incoming students. With Side of The Road, students can post their items easily and quickly. \\
In general, items are hard to find and often go to waste, as only the people who physically go down that street has a chance of seeing the item. Side of The Road aims to create a safe and reliable marketplace for college students. Existing  web/mobile applications like Craigslist and Letgo, allow users to very easily create new accounts to interface with the marketplace. However this causes an issue where new accounts are unable to be verified as said accounts could be bots or scammers. By using college/university email domains, we are able to easily verify if user is from the school and at the very least, is a real person. Craigslist also provides only general areas, e.g. Santa Cruz County, which covers large areas. Users would have to manually parse through listings to find ones close in proximity, while Side of The Road offers a radius option to filter large listings.

\section{Objective}
Side of The Road is used for sharing and locating items that have been placed on the side of the road that can be picked up for free or very cheap.

\subsection{General Lifecycle}

There are three lifecycles that our application must account for:

\noindent In the situation where a user wishes to get rid of or finds an item left on the side of the road: 
\begin{itemize}
	\item User opens the app
	\item Initial screen is a listing of items in a radius around the user
	\item The user can swipe right and access the camera function
	\item A picture can be taken, which will save the GPS of the user at that time
	\item A description can be added describing the item or circumstances around the item
	\item The post will be submitted and uploaded to the server
	\item The user's screen will then be directed back to the camera
\end{itemize}

In the situation where a user is looking for an item: 
\begin{itemize}
	\item User opens app
	\item User sets radius to filter item listings
	\item User scrolls through listings and finds something of interest
	\item User locates and takes item
	\item User marks item as taken 
\end{itemize} 

In the situation after an item has been posted:
\begin{itemize}
	\item Item is posted on app with timestamp
	\item Item will be removed if marked as taken
	\item Item will be removed if left for a long period of time
\end{itemize}

\subsection{Features}
Side of The Road offers many features:
\begin{enumerate}
	\item Authentication using Auth0 - Provides security for user information including name and 
	contact information
	\item Ability to upload photos and descriptions regarding the listing
	\item A map with thumbnails that provides an overview of listings in the area
	\item Some form of messaging to help alleviate the issue of sharing contact information - Some 	users may not want to share contact information like their email or phone number on the net.
	\item Posts that are removed after a user-specified time limit
\end{enumerate}

\noindent
Features, like authentication, will have more weight than others. Our main goal is to avoid bots from spamming the listings. This will keep our users happy and free from worrying about fake posts. Since interaction between users on Side of The Road are between strangers, we strive to keep contact information private. Direct message in the app will alleviate this and allow posters to help users with more information on an item. \\

\noindent
Some other features that may be offered depending on time constraints:
\begin{enumerate}
	\item Reporting posts to help control quality
	\item Easy sharing of a post
	\item Banning accounts
\end{enumerate}


\section{Users}
Side of The Road targets college students, specifically those that live in apartments. This app will be most beneficial to students looking for free/cheap items that other students no longer need. This may include: furniture, old electronics, textbooks, and etc. Although college faculty and departments are not the intended target users, Side of The Road may also be found useful for these users as excess equipment can be easily advertised for students (e.g. The surplus store on the UCSC campus is outdated and has little awareness)

\section{Timeline}
In order to develop Side of The Road, it will be split into three steps: basic functionality, posting, and viewing.
\textbf{(1)} Basic functionality will give the user the ability to maneuver to the login screen, item listings, and camera. This will also include accounts using Auth0 to enable creation and login of accounts.
\textbf{(2)} Posting will give include the picture of the item, the GPS location of the item, an option description, and a user set time-deletion of when the post should be removed. 
\textbf{(3)} Viewing will give users a list-based viewing of all items in the radius of the user. There will also be an option to view these listings as a thumbnail on a map. Items that have been taken will be marked and requires more than one user to authenticate if an item has been taken. Taken items will then be removed from the listing. \\




\end{document}
